---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `rscope`

<!-- badges: start -->
<!-- badges: end -->

`rscope` is an R package to simplify working with Gradescope rosters in R.

## Installation

You can install the development version of rscope from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("CarterZenke/rscope")
```

## Examples

`rscope` comes with 3 helper functions for working with gradebooks: `parse_lateness`, `find_and_parse_lateness`, and `select_assignments`.

### `parse_lateness`

Use `parse_lateness` to convert from Gradescope's `[H]H:MM:SS` format to seconds, minutes, or hours.

```{r parse_lateness_example}
library(rscope)
parse_lateness("1:00:00", unit = "seconds")
parse_lateness("12:30:10", unit = "minutes")
parse_lateness("3:15:04", unit = "hours")
```

### `find_and_parse_lateness`

Use `find_and_parse_lateness` to convert *all* of a roster's lateness columns to seconds, minutes, or hours.

```{r find_and_parse_lateness_example0}
library(rscope)
gradebook <- data.frame(`Problem Set 0: Scratch - Lateness (H:M:S)` = c("0:00:00", "1:32:11", "0:14:34"))
gradebook <- gradebook |> find_and_parse_lateness()
gradebook <- gradebook |> find_and_parse_lateness(unit = "minutes")
gradebook <- gradebook |> find_and_parse_lateness(unit = "hours")
```

By default, `find_and_parse_lateness` looks for "Lateness (H:M:S)" to identify a column as a lateness column, as this is Gradescope's default identifier. You can, though, adjust the regular expression yourself.

```{r find_and_parse_lateness_example1}
library(rscope)
gradebook <- data.frame(`pset0_scratch_late` = c("0:00:00", "1:32:11", "0:14:34"))
gradebook <- gradebook |> find_and_parse_lateness(regex = "late", unit = "seconds")
```

### `select_assignments`

Use `select_assignments` to return all columns that match an assignment's (or multiple assignments') title, in order, alongside the information that identifies students in your grade book.

```{r select_assignments_documentation}
library(rscope)
gradebook <- read.csv("tests/_datasets/gradescope_big_raw.csv", check.names = FALSE)
pset0 <- gradebook |> select_assignments("Problem Set 0")
problems <- gradebook |> select_assignments(c("Problem Set 0", "Problem Set 1", "Problem Set 2", "Problem Set 3"))
labs <- gradebook |> select_assignments(c("Lab 0", "Lab 1", "Lab 2", "Lab 3"))
```
